Completing this thesis has been one of the most challenging, yet fulfilling experiences I have had in my time here at Princeton. I could never have completed this alone and I am indebted to a long list of mentors, friends, and family.

First and foremost, I would like to express my gratitude to my advisor, Szymon Rusinkiewicz, whose support and advice has been invaluable throughout this entire process. Professor Rusinkiewicz went above and beyond what could be expected of an undergraduate thesis advisor and I appreciate how much I have learned from him, ever since my days of struggling through ``Death Graphics.'' I would also like to thank Professor Robert Stengel for his advice and support, as well as Professor Christopher Clark for introducing me to robotics and continuing to be a valuable source of advice during this project.

Furthermore, this project was funded by the School of Engineering and Applied Science, as well as the Morgan McKinzie $'$93 Senior Thesis Prize Fund. I am grateful to attend a school that makes projects such as this possible.

A special thanks goes to my thesis partner Sarah Tang. Her friendship and cheery disposition made those long hours of watching generally-uncooperative quadcopters a fun and memorable experience.

I would also like to thank everyone who made my time at Princeton incredible. In particular: my fellow hashers in the Princeton Tower Club for keeping my spirits up and providing wonderful distractions from my computer screen; my quasi-roommates and dinner companions, Nick Adkins and Alice Fuller, for bringing me so much happiness and laughter; John Subosits for indulging my pretending to be an engineer; Rodrigo and the rest of the Menezes family for claiming me as one of their own; Jonathan Yergler, Coach Zoltan Dudas, and the rest of the Princeton Fencing Team for all of the wonderful memories, both on and off the strip.

Finally, I would like to thank my parents. It is only with their love and support that I have made it to this point. I am unable to fully convey my appreciation for everything they have done.

